The ChEMBL database as Linked Open Data

### 2012-04-15 article.tex
Writing of the discussion section

Besides the PubMed identifiers used to link from literature references to Bio2RDF (see earlier),
ChEMBL uses DOIs alternatively, which we use to link out to the RDF provided by CrossRef~\citep{CrossRefRDF}:

@@

Egon,Antony/Valery,Ola: develop and write up the Bioclipse Decision Support use case

@@

outlook ...

@@

FIXME: add IMI

>>>>

Besides the PubMed identifiers used to link from literature references to Bio2RDF (see earlier),
ChEMBL uses DOIs alternatively, which we use to link out to the RDF provided by CrossRef~\citep{Bilder2011}:

@@

% Egon,Antony/Valery,Ola: develop and write up the Bioclipse Decision Support use case

@@

While we show here that the triple version of the ChEMBL data is very useful, the current triples are by no means static: ChEMBL-RDF
will keep evolve, following new developments in the Linked Open Data world. For example, it is likely that over time we will link out
to more Linked Data resources. More importantly, we wish to adopt more ontologies, of which the BioAssay Ontology is planned
next~\cite{Visser2011}.

@@
